```{r}
id <- ngRok::livestream_start(port = 8080, 
                              hostname = "www.rdaviscode.com",
                              password = 'nifflers', 
                              user = 'rdavis', scheme = 'http')
```

## Vocabulary  

Repo here: https://github.com/liza-wood/network-ladies

* Adjacency matrix: square matrix with the same names on 
* Incidence matrix: maybe a rectangular  

* Two-mode: only mode one to mode two, no intermode connections, formatted as mode one as rows and mode two as columns -- rectangular
* Bipartite: mode one can connect to mode one and mode two can connect to mode two, and mode one to mode two, so same rows and columns -- square  

* Multi-mode: multiple kinds of nodes; we think this just appears as a node attributes, in the end, since bipartite methods end up giving a level attribute to the node  
* Multi-plex: multiple kinds of edges  

```{r}
mat <- as.matrix(read.csv('data/ecoatlas_onemode.csv', row.names = 1))
```

```{r}
library(igraph)
library(network)
```

## Edgelists vs. matrics

In the end, all networks are matrices, and if you want to start with a matrix.  

It seems like igraph, by default, will give you the correct output. We needed to specify that weight = T for igraph, otherwise it seems to count more edges than there were.  

```{r}
?graph_from_adjacency_matrix
g_igraph <- graph_from_adjacency_matrix(mat, weighted = T)
g_igraph

?network
g_network <- network::network(mat, multiple = T)
g_network
```

What if we don't want it to be weighted?
```{r}
mat_uw <- ifelse(mat > 0, 1, 0)
g_network <- network::network(mat_uw, multiple = F)
# OR
g_network <- network::network(mat, ignore.eval = F, names.eval = 'weights')
g_network
```

## Plotting
```{r}
library(sna)
library(ggplot2)
library(GGally)
```

### gplot with `sna()`
```{r}
gplot(g_network)
```

### ggnet with `GGally()`
https://briatte.github.io/ggnet/#node-sizes 

```{r}
ggnet2(delete.vertices(g_network, isolates(g_network)), 
       size = "degree", legend.position = "none", 
       label = c("City.of.Foster.City", "California.State.Parks",
                 "City.of.Novato"),
       #edge.size = "weights",
       color = 'darkblue')
```

## Conclusions  
1. igraph is out, network objects are in  
2. adjacency are good to understand (necessary for more advanced analysis)  
3. lots of potential for `ggnet2` function to be the preferred plotting tool  